$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Added MSSM BM2 to table, added rest of parameters to table as well

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage{hyperref}
\usepackage{footmisc}
% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}
\usepackage{url}

@@

$\mu$ term contribution, as occurs in the MSSM.\\ \\ Demanding that

@@

\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cccc}
& MSSM & E$_6$SSM BM1 & E$_6$SSM BM2 \\
\hline
$\tan\beta(M_Z)$ & 10 & 10 & 10 \\
$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & 0.6 & 0.52 \\
$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & 0.2 & 0.13 \\
$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & 1313.0 \\
$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & 817.8 \\
$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -1103.2 \\
$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86\times 10^5$ & $2.04\times 10^6$ \\
$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 173.4 \\
$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 281.4 \\
$M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 175.2 \\
\hline
$M_{Z^\prime}$ [GeV] & $-$ & 2473.2 & 2512.7 \\
$m_{h_1}$ [GeV] & 124.3 & 125.0 & 126.2 \\
$m_{\tilde{t}_1}$ [GeV] & 1942.1 & 993.8 & 1665.0 \\
$m_{\tilde{t}_2}$ [GeV] & 2220.1 & 1174.8 & 2094.4 \\
$m_{\tilde{g}}$ [GeV] & 2259.8 & 2290.0 & 1407.4\\
\hline
$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 402.1 \\
$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 546.7
\end{tabular}
\end{ruledtabular}
\caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
BM1 and BM2. For the
E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
$B_{\mathrm{eff}}=A_\lambda$. In BM1 all other (diagonal) soft scalar squared masses not shown above are set to $(5\mathrm{ TeV})^2$, the soft trilinears $A_b$, $A_\tau=0$, $\mu^\prime=5000$ GeV and $B\mu^\prime=5000$ GeV$^2$. In BM2 the parameters not shown above are set to the values obtained by running the cE$_6$SSM point with $m_0=2.2$ TeV, $A_0=500$ GeV, $M_{1/2}=1003$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ to the SUSY scale, and setting $\mu^\prime(M_{\mathrm{SUSY}})=897.9$ GeV and $B\mu^\prime(M_{\mathrm{SUSY}})=-4.2\times10^5$ GeV$^2$.}
\label{tab:benchmarks}
\end{table}

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff.png} } \\
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}} \\
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Middle right panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.{\it Bottom right panel:} Individual sensitivities of MSSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.  {\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}
\usepackage{hyperref}
\usepackage{footmisc}
\usepackage{longtable}
% macros
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\SuperField}[1]{\hat{#1}}
\usepackage{url}

@@

$\mu$ term, as occurs in the MSSM.\\ \\ Demanding that

@@

\begingroup
\squeezetable
\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{ccccc}
& MSSM BM1 & MSSM BM2 & E$_6$SSM BM1 & E$_6$SSM BM2 \\
\hline
$\tan\beta(M_Z)$ & $10$ & $10$ & $10$ & $10$ \\
$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $6700$ & $6700$ \\
$\kappa_{1,2,3}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.6$ & $0.52$ \\
$\lambda_{1,2}(M_{\mathrm{SUSY}})$ & $-$ & $-$ & $0.2$ & $0.13$ \\
$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $689.7$ & $1013.5$ & $1093.3$ & $1313.0$ \\
$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & $345.7$ & $1032.5$ & $3792.7$ & $817.8$ \\
$A_\tau(M_{\mathrm{SUSY}})$ [GeV] & $0$ & $-5057.9$ & $0$ & $-88.5$ \\
$A_b(M_{\mathrm{SUSY}})$ [GeV] & $0$ & $-5707.2$ & $0$ & $-1720.7$\\
$A_t(M_{\mathrm{SUSY}})$ [GeV] & $-3335.7$ & $-2734.8$ & $-1100$ & $-1103.2$ \\
$m_{L1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.35\times 10^6$ & $2.5\times 10^7$ & $4.94\times 10^6$ \\
$m_{L3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.22\times 10^6$ & $2.5\times 10^7$ & $4.90\times 10^6$ \\
$m_{e1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.27\times 10^6$ & $2.5\times 10^7$ & $5.21\times 10^6$ \\
$m_{e3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $6.03\times 10^6$ & $2.5\times 10^7$ & $5.11\times 10^6$ \\
$m_{Q1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.37\times 10^6$ & $2.5\times 10^7$ & $5.76\times 10^6$ \\
$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45\times 10^6$ & $3.97\times 10^6$ & $4.50\times 10^5$ & $3.61\times 10^6$ \\
$m_{u1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.54\times 10^6$ \\
$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.0 \times 10^6$ & $6.60\times10^5$& $5.86\times 10^5$ & $2.04\times 10^6$ \\
$m_{d1,2}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.30\times 10^6$ & $2.5\times 10^7$ & $5.88\times 10^6$ \\
$m_{d3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $2.5\times 10^7$ & $7.03\times 10^6$ & $2.5\times 10^7$ & $5.78\times 10^6$ \\
$m_{H_d}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
$m_{H_u}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & & & & \\
$m_S^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $-$ & $-$ & & \\
$M_1(M_{\mathrm{SUSY}})$ [GeV] & $300$ & $260.8$ & $300$ & $173.4$ \\
$M_2(M_{\mathrm{SUSY}})$ [GeV] & $2000$ & $479.2$ & $1050$ & $281.4$ \\
$M_3(M_{\mathrm{SUSY}})$ [GeV] & $2000$ & $1312.3$ & $2000$ & $1200$ \\
$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & $-$ & $300$ & $175.2$ \\
\hline
$M_{Z^\prime}$ [GeV] & $-$ & $-$ & $2473.2$ & $2512.7$ \\
$m_{h_1}$ [GeV] & $124.3$ & $124.4$ & $125.0$ & $126.2$ \\
$m_{\tilde{t}_1}$ [GeV] & $1942.1$ & $861.6$ & $993.8$ & $1665.0$ \\
$m_{\tilde{t}_2}$ [GeV] & $2220.1$ & $2023.9$ & $1174.8$ & $2094.4$ \\
$m_{\tilde{g}}$ [GeV] & $2259.8$ & $1472.9$ & $2290.0$ & $1407.4$ \\
\hline
$\Delta(M_X=20\textrm{ TeV})$ & $157.3$ & $242.8$ & $165.3$ & $402.1$ \\
$\Delta(M_X=10^{16}\textrm{ GeV})$ & $1089.0$ & $949.0$ & $1722.3$ & $546.7$
\end{tabular}
\end{ruledtabular}
\caption{Parameters for the MSSM and E$_6$SSM benchmark points. In the E$_6$SSM we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
$B_{\mathrm{eff}}=A_\lambda$. The soft masses $m_{H_d}^2$, $m_{H_u}^2$ and $m_S^2$ are those that satisfy the EWSB conditions including 1-loop Coleman-Weinberg corrections involving the top and stops. For E$_6$SSM BM1 (BM2) we also set $\mu^\prime = 5000.0$ $(897.9)$ GeV, $B\mu^\prime = 5000.0$ $(-4.21\times 10^5)$ GeV$^2$, $A_{\kappa 1,2,3} = 0$ $(-1389.2)$ GeV, $A_{\lambda 1,2} = 0$ $(-52.9)$ GeV, $m_{D1,2,3}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{\overline{D}1,2,3}^2 = 2.5\times 10^7$ $(4.90\times 10^6)$ GeV$^2$, $m_{H^d_{1,2}}^2 = 2.5\times 10^7$ $(4.46\times 10^6)$ GeV$^2$, $m_{H^u_{1,2}}^2 = 2.5\times 10^7$ $(4.81\times 10^6)$ GeV$^2$, $m_{S_{1,2}}^2 = 2.5\times 10^7$ $(5.28\times 10^6)$ GeV$^2$, $m_{H'}^2 = 2.5\times 10^7$ $(4.94\times 10^6)$ GeV$^2$ and $m_{\overline{H'}}^2 = 2.5\times 10^7$ $(4.87\times 10^6)$ GeV$^2$.
}
\label{tab:benchmarks}
\end{table}
\endgroup
\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_4_benchmark_points_tuning_vs_cutoff.png} } \\
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}} \\
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Middle left panel:}  Individual sensitivities of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Middle right panel:} Individual sensitivities of E$_6$SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.{\it Bottom right panel:} Individual sensitivities of MSSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.  {\it Bottom right panel:} Individual sensitivities of E$_6$SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
